Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?

### 2022-09-30 Paper.Rmd
first pass is complete!

Negativity Bias Theorem and Prospect Theory had a strong support in the case of search goods. The regression results showed that the reviews which had low ratings and/or reviews which had more negative words in them were found to be more helpful on the average. Additionally, Perceived Helpfulness has higher responsiveness to Review Length when a review has a low rating. This means that people focus more on negative cues than positive cues probably because they want to cut down potential sure losses. A similar result was reflected by the negative coefficient of the proportion of positive words in a review. This shows that reviews with positive sentiments doesn't have a strong diagnostic value for consumers. Nonetheless, the U-Shape of the Review Rating variable also suggests positivity bias [@hoorens2014]. An explanation to this could be that certain brands or products might be favored by some customers and these customers might selectively tend towards positively rated reviews and find them helpful just because they love the brand [@zhu2021]. The reason why there is a divergence between the "positively rated review" and "a review with positive sentiment" might be explained by this. A consumer who has brand or product inclinations wants to be persuaded to have the product so this particular consumer doesn't really care about what is written in the review, he might skim through positive reviews until he feels persuaded. Since a preference towards a brand is subjective it might be speculated that a strong brand image could embed experience attributes into search goods. A similar notion was discussed by @mudambi2010 where they classified Apple iPod as an experience good. That is although an MP3 player such as iPod has many objective search attributes such as storage capacity and battery life, what makes this particular product preferable most of the time is the product image that was created by Apple.

@@

-   more elab is needed here
-   you can discuss about the fluidity of search and exp attributes

A similar strong support for Negativity Bias can't be observed in the case of movies. Only evidence for Negativity Bias was the significant linear interaction term between Review Length and Review Rating. According to this result the U-Shaped function of Review Rating is only observable when Review Length is high enough. This is actually the case for search goods as well but the interaction term doesn't interfere with the sign of the other coefficients so no matter the Review Length is U-Shaped function is observed. However, this is certain that as the review rating gets higher the review loses its diagnostic value for both for experience and search goods because the coefficient of the Review Length weakens. This means that potential buyers require more elaboration when a review is rated low. For experience goods, high rated reviews become more helpful on the average when reviews are short. This also might be a sign for positivity bias where people pay more attention to reviews which were aligned with their own feelings [@zhu2021]. Since experience attributes are naturally subjective it is logical to think that readers look for reviews that they agree.

@@

Another reason may arise from the subjective nature of the experience attributes of the movies. Negative words, in the case of electronics, may have narrower range of meanings because what they usually try to convey directly relates the to quality of the good itself. The quality of the good is easily accessible because of the fact that electronics have dominant search attributes. Thus, negative words probably translates as potential monetary risks rather than affecting emotions. A risk might be exemplified as purchasing a sub-par performing laptop with a given budget, in other words getting sub-optimal utility. Furthermore, electronics are usually bought to be used for a comparatively long period of time. A smartphone or a television can serve its owner for years so negative cues which relate to below average durability are very important. Buying a sub-durable product for a given budget can only increase the chances that the consumer will have to buy the same type of product prematurely in the future. On the other hand, the monetary risks associated with a bad movie are relatively lower. Consumers can go to cinema, buy a DVD or access the movie as a part of their subscription plan on platforms such as Netflix. Subscription or ticket fees aren't the only cost for the consumer. In order to consume the product the consumer must spend the time that is equal to the duration of the movie. Of course, the consumer can stop watching the movie anytime if it is too unbearable for her so she doesn't waste any more time. Because of these reasons the money spent on a movie might be irrelevant to an average consumer since accessing a movie is relatively cheaper than owning an electronic device. Therefore, negative words in a movie review may not alert the consumer for potential monetary losses. Instead, negative words could render a review in question unpleasant because emotions are priority in the case of consumption of movies.

@@

\*\*WORK IN PROGRESS\*\*

\*\*WORK IN PROGRESS\*\*

\*\*WORK IN PROGRESS\*\*

\*\*WORK IN PROGRESS\*\*

>>>>

Negativity Bias Theorem and Prospect Theory had a strong support in the case of search goods. The regression results showed that the reviews which had low ratings and/or reviews which had more negative words in them were found to be more helpful on the average. Additionally, Perceived Helpfulness has higher responsiveness to Review Length when a review has a low rating. This means that people focus more on negative cues than positive cues because the marginal value of additional negative information is higher. This way they are able to cut down potential sure losses. A similar result was reflected by the negative coefficient of the proportion of positive words in a review. This shows that reviews with positive sentiments don't offer diagnostic value for consumers. Nonetheless, the U-Shape of the Review Rating variable also suggests positivity bias [@hoorens2014]. An explanation to this could be that certain brands or products might be favored by some customers and these customers might selectively tend towards positively rated reviews and find them helpful just because they love the brand [@zhu2021]. The reason why there is a divergence between the "positively rated review" and "a review with positive sentiment" might be explained by this. A consumer who has brand or product inclinations wants to be persuaded to have the product so this particular consumer doesn't really care about what is written in the review, he might skim through positive reviews until he feels persuaded. Since a preference towards a brand is subjective it might be speculated that a strong brand image could embed experience attributes into search goods. A similar notion was discussed by @mudambi2010 where they classified Apple iPod as an experience good. That is although an MP3 player such as iPod has many objective search attributes such as storage capacity and battery life, what makes this particular product preferable most of the time is the product image that was created by Apple.

@@

-   more elab is needed here
-   you can discuss about the fluidity of search and exp attributes, tv is an experience goods in the original work

A similar strong support for Negativity Bias can't be observed in the case of movies. Only evidence for Negativity Bias was the significant linear interaction term between Review Length and Review Rating. According to this result the U-Shaped function of Review Rating is only observable when Review Length is high enough. A similar situation is the case for search goods as well but the interaction term doesn't interfere with the signs of the other coefficients so no matter the Review Length is a U-Shaped function is observed for search goods. However, this is certain that as the review rating gets higher the review loses its diagnostic value for both for experience and search goods because the coefficient of the Review Length weakens. This means that potential buyers require more elaboration when a review is rated low. For experience goods, high rated reviews become more helpful on the average when reviews are short. This also might be a sign for positivity bias where people pay more attention to reviews which were aligned with their own feelings [@zhu2021]. Since experience attributes are naturally subjective it is logical to think that readers look for reviews that they agree.

@@

Another reason may arise from the subjective nature of the experience attributes of the movies. Negative words, in the case of electronics, may have narrower range of meanings because what they usually try to convey directly relates the to quality of the good itself. The quality of the good is easily accessible because of the fact that electronics have dominant search attributes. Thus, negative words probably translates as potential monetary risks rather than affecting emotions. A risk might be exemplified as purchasing a sub-par performing laptop with a given budget, in other words getting sub-optimal utility. Furthermore, electronics are usually bought to be used for a comparatively long period of time. A smartphone or a television can serve its owner for years so negative cues which relate to below average durability are very important. Buying a sub-durable product for a given budget can only increase the chances that the consumer will have to buy the same type of product prematurely in the future. On the other hand, the monetary risks associated with a bad movie are relatively lower. Consumers can go to cinema, buy a DVD, rent the movie on YouTube or access the movie as a part of their subscription plan on platforms such as Netflix. Subscription or ticket fees aren't the only cost for the consumer. In order to consume the product the consumer must spend the time that is equal to the duration of the movie. Of course, the consumer can stop watching the movie anytime if it is too unbearable for her so she doesn't waste any more time. Because of these reasons the money spent on a movie might be irrelevant to an average consumer since accessing a movie is relatively cheaper than owning an electronic device. Therefore, negative words in a movie review may not alert the consumer for potential monetary losses. Instead, negative words could render a review in question unpleasant because emotions are priority in the case of consumption of movies.

@@

This study collected Online Customer Reviews data from two different sources (IMDB and BestBuy) and analyzed the data within the context of consumer uncertainty. Negativity Bias Theorem, Prospect Theory and Search / Experience goods paradigm from information economics were used as an theoretical engine to explain the information gathering process of a consumer. Results showed similarities from the existing Review Helpfulness literature. However, once again it should be noted that the literature has many conflicting results.

This study contributes to the literature as an additional empirical work with a unique BestBuy review data and a unique combination of movie reviews from IMDB. In addition, to my knowledge, this the first study which analyzed the linear interaction between Review Length and Review Rating in terms of Negativity Bias Theorem.

Goods with very strong search or experience attributes were chosen in order to compare the information gathering process in the clearest way possible. The results proves the fact that information gathering is easier for search goods than experience goods. This means that consumers face less uncertainty against search goods. The results are only generalizable to laptops, phones, televisions and movies since different goods have different mix of search and experience attributes.

There are some implications for future studies. Firstly, aside from lexicon based sentiment analysis it is also possible to utilize deep learning methods to mine opinions from a text. One advantage of deep learning method over a lexicon is its versatility. A negative word can change from one context to another and training a deep learning method is more robust to this type of contextual changes whereas with lexicons a negative word is a negative word no matter the context is. Secondly, future studies should consider collecting data from different regions and cultures. There might be some differences on how consumers process and react to the information in order to deal with uncertainty. Lastly, researchers can dig deeper into search and experience goods paradigm. It is well established in the literature that product type affects the information gathering process. However, there might be differences within product types depending on their search and experience attributes. An objective way to identify and index experience and search attributes may also shed some light to the conflicting results in the literature.
